---
title: "RIntro"
output:
  pdf_document: default
  html_document: default
urlcolor: blue
---
RIntro.rmd: First prints a hello world line, then start doing some basic data manipulation. 
(Knitted PDF attached)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

----

Prints out something, hopefully, hello world.

```{r}
print("Hello world!")
```

(EXTENSION) As R is a data-analysis language, I decided to try manipulate some simple operations on a dataset. From a famous dataset I grabbed a nutrition study. Let's look at it: it contains data on 315 patients undergoing elective surgery, among which are personal characteristics, dietary habits, and plasma concentrations of retinol, beta-carotene, and other cartenoids.

```{r load-data}
library(Lock5Data)
data("NutritionStudy")
```

We could see the structure with the function `str()`.

```{r}
str(NutritionStudy)
```

In the blank code chunk below we generate a 5-number summary the variable `Age`.

```{r}
summary(NutritionStudy$Age)
```

Use the blank code chunk below to find the mean and the median for the variable `Cholesterol`.

```{r}
mean(NutritionStudy$Cholesterol)
median(NutritionStudy$Cholesterol)
```

We use the command `hist()` to view the distribution of the `Cholesterol` variable, with assigned bin value.

```{r}
hist(NutritionStudy$Age, breaks = c(10, 20, 30, 40, 50, 60, 70, 80, 90))
hist(NutritionStudy$Cholesterol, breaks = c(0, 200, 400, 600, 800, 1000))
```